Title of submission to PLOS journal

### 2019-08-22 docs/manuscript_draft.tex
update temp ms

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Title of submission to PLOS journal} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Alice Anonymous\textsuperscript{\getAff{Some Institute of Technology}}\textsuperscript{*},
Bob Security\textsuperscript{\getAff{Another University}}\\
\bigskip
\textbf{\getAff{Some Institute of Technology}}Department, Street, City, State, Zip\\
\textbf{\getAff{Another University}}Department, Street, City, State, Zip\\
\bigskip
* Corresponding author: alice@example.com\\
\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur eget
porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut
dui eu ante cursus gravida non sed sem. Nullam sapien tellus, commodo id
velit id, eleifend volutpat quam. Phasellus mauris velit, dapibus
finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium
diam, quis maximus dolor faucibus id. Nunc convallis sodales ante, ut
ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit
pulvinar, volutpat risus.

@@

\includegraphics[width=360px]{../../figures/images/PigeonHPGaxis}

@@

\includegraphics[width=360px]{../../figures/images/samplingtimepoints}

@@

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

@@

@@

\hypertarget{about-the-authors}{%
\subsection{About the authors}\label{about-the-authors}}

Roles, Affiliations, Orcids, competing interests

>>>>

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Title of submission to PLOS journal} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Alice Anonymous\textsuperscript{\getAff{Some Institute of Technology}}\textsuperscript{*},
Bob Security\textsuperscript{\getAff{Another University}}\\
\bigskip
\textbf{\getAff{Some Institute of Technology}}Department, Street, City, State, Zip\\
\textbf{\getAff{Another University}}Department, Street, City, State, Zip\\
\bigskip
* Corresponding author: alice@example.com\\
\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
Lorem ipsum dolor sit amet, consectetur adipiscing elit.

@@

\includegraphics[width=360px]{../figures/images/PigeonHPGaxis}

@@

\includegraphics[width=360px]{../figures/images/samplingtimepoints}

@@

@@

\hypertarget{wgcna-characterization}{%
\subsection{WGCNA characterization}\label{wgcna-characterization}}

This first image was made using
\href{https://github.com/macmanes-lab/DoveParentsRNAseq/blob/master/analysis/08_WGCNA_1.R}{\texttt{08\_WGCNA\_1.R}},
which was modified from the
\href{https://horvath.genetics.ucla.edu/html/CoexpressionNetwork/Rpackages/WGCNA/Tutorials/Consensus-DataInput.R}{first
in a series of WGCNA tutorial}. The first tutorial focuses on data
input, cleaning and pre-processing; outlier removal; clustering of
samples by their Euclidean distance; a comparison of sample cluster to
sample meta data.

\includegraphics{manuscript_draft_files/figure-latex/wgcna-1.pdf}

@@
